### 2024-08-06 cluster-analysis.qmd
20240730 - REF
20240806 - overview of cluster analysis approaches

There are many approaches to cluster analysis, including model-based clustering, density-based clustering, centroid-based clustering, etc.
In this chapter, we focus on examples using model-based clustering with the `mclust` package, which uses Gaussian finite mixture modeling.

>>>>

There are many approaches to cluster analysis, including model-based clustering, density-based clustering, centroid-based clustering, hierarchical clustering (aka connectivity-based clustering), etc.
An overview of approaches to cluster analysis in `R` is provided by @Kassambara2017a.
In this chapter, we focus on examples using model-based clustering with the `mclust` package [@Scrucca2023], which uses Gaussian finite mixture modeling.
